SylvanSeeds, a seed germination database for temperate deciduous forests

### 2020-06-30 doc/ms/v4_JVS/cover-letter.Rmd
JVS submission

---
title: "Cover letter"
author: "Eduardo Fernández Pascual"
date: "20/6/2020"
output: pdf_document
bibliography: refs.bib
csl: new-phytologist.csl
link-citations: yes
always_allow_html: true
---

@@

I submit my manuscript *SylvanSeeds, a database and web app to explore seed germination in temperate broadleaf and mixed forests* to be considered for publication as a **Methods** paper in New Phytologist.

## What hypotheses or questions does this work address?

This is a methods paper describing *SylvanSeeds*, a database and web app (http://sylvanseeds.shinyapps.io/sylvanseeds/) of raw germination records for frequent species of temperate deciduous and mixed forests. The list of frequent species was created using 17,852 vegetation relevés from the sPlot database [@RN4658].

## How does this work advance our current understanding of plant science?

@@

## Why is this work important and timely?

>>>>

---
title: "Cover letter"
author: "Eduardo Fernández-Pascual"
date: "20/6/2020"
output: pdf_document
bibliography: refs.bib
csl: journal-of-vegetation-science.csl
link-citations: yes
always_allow_html: true
---

@@

I submit my manuscript *SylvanSeeds, a seed germination database for temperate deciduous forests* to be considered for publication as a **Report** in the Journal of Vegetation Science. This is a first submission to JVS and it comprises work that has not been published, and is not being considered for publication elsewhere.

This report describes *SylvanSeeds*, a database and web app (https://efernandezpascual.shinyapps.io/sylvanseeds/) of raw germination records for frequent species of temperate broadleaf and mixed forests. The list of frequent species was created using 17,852 vegetation relevés from the sPlot database [@RN4658].

@@

### 2020-06-30 doc/ms/v4_JVS/ms.Rmd
JVS submission

---
title: "SylvanSeeds, a database and web app to explore seed germination in temperate broadleaf and mixed forests"
subtitle: "Running title: SylvanSeeds, a forest germination database"
output: 
  bookdown::word_document2:
    reference_docx: template.docx
bibliography: refs.bib
csl: new-phytologist.csl
link-citations: yes
always_allow_html: true
---

@@

**Total word count** 2,578 **Introduction** 530 **Materials and Methods** 968 **Results** 848 **Discussion** 226 **Number of figures** 2 in colour **Tables** 0 **Supporting information** 6

# Summary

* Seed traits have functional significance in all levels of plant biology, but there is a lack of germination databases of wide geographical scope. This article presents *SylvanSeeds*, a first global dataset of germination records for an ecologically coherent unit: Temperate Broadleaf and Mixed Forests.

* Data were gathered with a systematic literature search. A list of frequent taxa of the study area was created using `r MSplots` vegetation relevés from the sPlot database. The list was searched in the Web of Science. 6,791 references were screened, finding 614 articles from which data were extracted.

* *SylvanSeeds* includes `r MSrecords` germination records of `r MSspecies` species from `r MSfamilies` families (gymnosperms and angiosperms), collected in 46 countries between 1920-2017. It provides raw data for meta-analysis: proportions of seeds germinated in laboratory experiments of scarification, stratification, light-darkness, and constant-alternating temperatures. *SylvanSeeds* is freely distributed as a *.csv*. The shiny app *SylvanSeeds* is also presented, to make data accessible to the public.

* *SylvanSeeds* advances functional seed ecology and brings two innovations to plant science.  First, the data-gathering methodology can be extended to other biomes. Second, database and app can be a standard in further efforts to compile germination data.

**Keywords:** germination database, germination temperature, light and dark germination, seed dormancy, seed traits, temperate coniferous forests, temperate deciduous forests, temperate evergreen forests

@@

Seed traits have functional significance in all levels of plant biology, from population dynamics [@RN3043] to community assembly [@RN2942] and species distributions [@RN2942]. Recent discussions [@RN2352; @RN4655] highlighted the lack of reliable germination databases of wide geographical scope as a major limitation to produce a global synthesis of the seed ecological spectrum. Seed germination is the first major developmental transition in the life of a plant, and it has profound effects on the plant's ecology [@RN2384]. As such, the timing of this transition is controlled by a combination of environmental signals. Amongst these are temperature [@RN2249], diurnal temperature alternation [@RN2217], light [@RN4656] and seed dormancy inductors and relievers [@RN3063]. All of these signals interact to produce a coarse- and fine-scale regulation of germination timing, integrating inputs from both seasonal climatic cycles [@RN3132] and local environmental gradients [@RN2865]. The practical consequence of this is that the response of seeds to, for example, light will depend on other conditions set by the experimenter. This makes it difficult to summarise germination “traits” into a single value in a way comparable to seed mass, specific leaf area or plant height [@RN2923], and may explain the lack of global germination databases. Germination compilations with a biogeographical background, of which the prime example today is the cornerstone book of Baskin and Baskin [-@RN3214], only provide summary information, for instance the interpreted optimal germination temperature instead of the proportion of seeds germinated across a temperature gradient.

To fill this gap, this article presents *SylvanSeeds*, a first global dataset of raw germination data for an ecologically and biogeographically coherent unit: the Temperate Broadleaf and Mixed Forests biome of the northern hemisphere (*TBMFNH*). The building of the dataset was part of a research project conducted within the *sPlot* initiative [@RN4658], specifically *sPlot*’s project #12 (https://www.idiv.de/en/sdiv/working_groups/wg_pool/splot/projects.html). The goal of *sPlot* #12 was to study taxonomical and functional plant diversity in deciduous forests, which are dominant in temperate latitudes with mild to cold winters and relatively warm and wet summers. In the northern hemisphere, they also form a coherent evolutionary and biogeographic unit, sharing a common Tertiary history until they became separated between North America, Asia and Europe [@RN4684]. At the same time, a relatively high number of classic seed biology research groups have worked within the *TBMFNH* areas, e.g. in the USA [@RN1045], the UK [@RN3273], Belgium [@RN656] and Japan [@RN1188]. For this reason, *sPlot* project #12 was chosen to incorporate a biome-wide analysis of seed traits, as it was expected that the *TBMFNH* would provide a wide scope of available data. To gather data for the project, a systematic literature search [@RN2401] was applied to a list of frequent species representing the flora of the *TBMFNH*. This data paper makes the database accessible to the research community. Additionally, the *SylvanSeeds* shiny web app is presented to facilitate the exploration of the data.

@@

The list of frequent species (plus the synonyms recorded in the relevés) was incorporated into a Boolean search string, together with the words "(seed OR seeds) AND (dormancy OR germination)” (**Supporting Information 1**). This string was searched in the *Thompson Reuters Web of Science* on 5 Mar 2019, returning 6,791 results. The processing of these results is described in a PRISMA flow diagram (**Supporting Information 2**). A first filter of the results by the relevance of the title retained 1,489 references. An effort was made to access the full text of all these references, using in order the following channels: (i) “Find Full Text” functionality in *EndNote X9*, (ii) online access to the journals using the institutional subscriptions of the University of Oviedo; (iii) request to the authors through *ResearchGate*; (iv) general search of *pdf* files in *Google* using the article details. Unfortunately, 236 references could not be accessed. Most of these belonged to smaller publishers not included in the subscriptions of the University of Oviedo, and to older journal volumes which had not been digitalised. The resources of this project did not make it possible to further pursue these references, but they are included as a *BibTeX* file (**Supporting Information 3**) in case they can be processed in the future. The found texts were accessed to retrieve data for the database. At this stage, references were considered to be non-relevant if they (i) did not pertain to species in the original frequent species list; (ii) did not study germination in species monocultures (e.g. competition studies); (iii) did not report the minimal information needed (number of seeds sown, germination percentage and germination temperature). Records were also excluded when they pertained to special germination treatments that do not allow for general comparisons (i.e. use of germination promoters such as the plant hormone gibberellic acid; drought treatments, including polyethylene glycol solutions; application of heavy metals or other pollutants; smoke-related germination promoters such as karrikins). Of the accessed references, 639 were non-relevant (*BiBTeX* file in **Supporting Information 4**) and 614 provided relevant data (*BiBTeX* file in **Supporting Information 5**).

@@

For each relevant reference, three blocks of information were recorded. The first block described the plant material, including the species, the populations that had been sampled, the year of sampling (or the year of publication if that information was missing), the country, the geographical coordinates (if not provided in the reference, the closest available toponyms were searched in *Google Maps*; in some cases the only geographical information was the country, in these cases the coordinates of the capital were recorded). The second block described the experimental conditions: experimental setting (greenhouse, incubator or room temperature), germination substrate and characteristics of the containers, seed storage, application of seed sterilization or nutrients, length of the germination incubations, use of stratification (none, cold [< 15ºC], warm [>= 15ºC] or combinations of cold and warm), use of scarification, photoperiod, maximum germination temperature, minimum germination temperature, and weighted average germination temperature. The third block contained the final germination proportion: the reported final germination percentages (retrieved from the text, tables or figures) and the reported number of replicates and seeds per replicate were used to calculate a count of seeds sown and a count of seeds germinated.

@@

The final database contains `r MSrecords` records (germination proportions for a given seed lot of a species, recorded in a set of experimental conditions) from 614 references. The plant materials had been collected across the Temperate Broadleaf and Mixed Forest biome and surrounding areas (**Fig. \@ref(fig:fig1)**) in both hemispheres. The oldest record was from 1920 and the top three contributing countries were the USA (`r MScountries[1, 2]`), the UK (`r MScountries[2, 2]`) and Japan (`r MScountries[3, 2]`). There were `r MSspecies` species represented, from `r MSfamilies` seed plant families. The total estimate of seeds used in the experiments was `r MSseeds`. The range of germination temperatures (weighted average of the daily thermoperiod) went from `r MSminT` to `r MSmaxT` ºC, with `r MSaltY` records of constant temperatures and `r MSaltN` of alternating temperatures. Light was used in `r MSlightY` records, darkness in `r MSlightN` and `r MSlightNA` did not provide information on this parameter. The experiments were performed with unstratified seeds in `r MSstratN` records, and of the rest, the majority (`r MSstratCold`) went through cold stratification. Scarification was applied to `r MSscarY` records.

@@

The database is provided as a *csv* file, comma separated, named **Supporting Information 6** (see online Supporting Information). The first row of the file contains the header data, with the following variables: *Taxon* (the original species names, as used in the references), *TPLName* (*The Plant List* species names), *Family* (the botanical family of the species), *Reference* (bibliographic source of the record), *Year* (year the seed lot was collected), *Country* (country where the seed lot was collected), *Population* (geographical information of the seed lot), *Latitude* (approximated latitude where the seed lot was collected, in decimal degrees), *Longitude* (approximated longitude where the seed lot was collected, in decimal degrees), *Dry_storage* (binary variable indicating whether the seed lot was kept at dry storage for more than a month between seed collection and start of the experiments), *Setting* (environs used to control germination temperature: either a greenhouse, a climatically-controlled incubator, or room temperature), *Sterilization* (note on surface sterilization treatments applied to the seed lot before the experiments), *Nutrients* (note on nutrient application to the germination substrate), *Substrate* (substrate used to hold the seeds during the germination incubation), *Container_type* (type of container used to hold the substrate and the seeds during the experiments), *Container_size* (dimensions of the germination containers), *Container_number* (number of germination containers used for the treatment), *Sown_by_container* (number of seeds sown in each container), *Incubation_days* (number of days between the start of the experiment, not including stratification, and the day when germinated seeds were counted), *Scarification* (binary variable indicating whether the seed lot was scarified before the test), *Stratification_days* (number of days the seed lot was exposed to any type of stratification, before the test), *Stratification_temperature* (temperature or temperatures used during the stratification treatment, in degrees Celsius), *Stratification_type* (type of stratification, which can be none, cold, warm or combinations of cold and warm), *Stratification* (binary variable indicating whether the seed lot was stratified or not before the test), *Light* (binary variable indicating whether the seed lot was germinated in light or in darkness), *Photoperiod* (number of hours of exposure to light in the daily photoperiod), *Alternating* (binary variable indicating whether the germination test was conducted under constant or alternating temperatures), *Tdif* (difference in degrees between the hottest and the coldest temperatures of the daily thermoperiod), *Tmax* (hottest temperature in the daily thermoperiod), *Tmin* (coldest temperature in the daily thermoperiod), *Tmean* (mean germination temperature, weighted by the length of each phase of the daily thermoperiod), *Temperature* (aggregation of the mean germination temperature in 5 ºC intervals), *Germinated* (count of seeds that germinated during the experiment), *Germinable* (count of seeds used in the experiment). Each row below the header represents a record for a seed lot germinated in a given set of experimental conditions. Presenting the response variable as a proportion (i.e. number of successes *Germinated*, number of trials *Germinable*) has important benefits for meta-analysis of the database, as proportions can be analysed directly using a GLM, and a variance term does not need to be specified since it is incorporated as part of the analysis [@RN4751].

@@

To facilitate the visualization of the database, the *SylvanSeeds* app was written using the *shiny* package [@RN4661]. It is publicly accessible at http://sylvanseeds.shinyapps.io/sylvanseeds/. The app uses the *tidyverse* package [@RN4662] to aggregate and show results for species and experimental treatments (i.e. aggregating all seed lots of the same species germinated in the same experimental conditions). To facilitate comparisons, germination temperatures are aggregated to 5 ºC intervals. When there is only one seed lot per species and combination of experimental conditions, the binomial 95% confidence interval is calculated using the Wilson method in the *binom* package [@RN2964]. When there is more than one seed lot per species and combination of experimental conditions, the aggregate proportion and binomial confidence intervals are calculated using binomial-normal meta-analysis models [@RN4663] as implemented in the package *metafor* [@RN2274]. By visiting the app, users can consult the available germination information for a species (**Fig. \@ref(fig:fig2)**), the origin of its seed lots, and the bibliographical references for the species.

@@

The database provided in this article, and the web app to visualize it, can have wide applicability in science and beyond. It can extend current trends in global analyses of plant traits at species [@RN3318] and community levels [@RN4664] to seed germination. The ecological determinants of seed germination are also valuable information for species distribution models [@RN3078]. The visualization of the database with the *SylvanSeeds* app can help plant ecologists select experimental treatments that are adequate for their experiments [@RN2999]. Outside of academia, germination data are useful for seed industries [@RN4665], restoration practitioners [@RN2241] and the implementation of regional schemes for seed-based landscape intervention [@RN4666]. The app is accessible to citizens in general who are interested in germinating wild plants. Finally, apart from the dataset itself, this article can bring two innovations to the seed ecology community, helping to advance the agenda of functional seed ecology [@RN4655]. First, the meta-analysis-inspired methodology used to compile the dataset can be extended to other biomes and lists of species, contributing to the creation of a global database for ecologically and biogeographically coherent floras. Second, the database and the app can serve as a standard in further efforts to compile and standardize seed germination data.

@@

# Author Contribution

This is a single-author article.

@@

**Supporting Information 1** Boolean search string used in the Web of Science. **Supporting Information 2** PRISMA 2009 flow chart describing the process of reference screening and inclusion. **Supporting Information 3** BibTeX bibliography listing the not found full texts.  **Supporting Information 4** BibTeX bibliography listing the non-relevant references.  **Supporting Information 5** BibTeX bibliography listing relevant references included in the *SylvanSeeds* database.  **Supporting Information 6** *SylvanSeeds* database in a single *.csv* file.

@@

All persons can use the database providing they cite this paper properly in any publications or in the metadata of any derived products that are produced using the database. The database is provided as Supporting Information. It can be visualized with the *SylvanSeeds* app at http://sylvanseeds.shinyapps.io/sylvanseeds/. The code of the app is stored at (note: the GitHub repo is kept private until publication of the manuscript).

>>>>

---
title: "SylvanSeeds, a seed germination database for temperate deciduous forests"
subtitle: "Running title: SylvanSeeds, a forest germination database"
output: 
  bookdown::word_document2:
    reference_docx: template.docx
bibliography: refs.bib
csl: journal-of-vegetation-science.csl
link-citations: yes
always_allow_html: true
---

@@

# Abstract

Seed traits have functional significance in all levels of plant biology, but there is a lack of germination databases of wide geographical scope. This article presents *SylvanSeeds*, a first global database of germination records for an ecologically coherent unit: Temperate Broadleaf and Mixed Forests. Data were gathered with a systematic literature search. A list of frequent taxa of the study area was created using `r MSplots` vegetation relevés from the sPlot database. The list was searched in the Web of Science. 6,791 references were screened, finding 614 articles from which data were extracted. *SylvanSeeds* includes `r MSrecords` germination records of `r MSspecies` species from `r MSfamilies` families (gymnosperms and angiosperms), collected in 46 countries between 1920-2017. It provides raw data for meta-analysis: proportions of seeds germinated in laboratory experiments of scarification, stratification, light-darkness, and constant-alternating temperatures. *SylvanSeeds* is freely distributed as a *.csv*. The shiny app *SylvanSeeds* (https://efernandezpascual.shinyapps.io/sylvanseeds/) is also presented, to make data accessible to the public. *SylvanSeeds* advances functional seed ecology and brings two innovations to plant science.  First, the data-gathering methodology can be extended to other biomes. Second, database and app can be a standard in further efforts to compile germination data.

**Keywords:** germination database, germination temperature, light and dark germination, seed dormancy, seed traits, temperate coniferous forests, temperate broadleaf and mixed forests, temperate evergreen forests

@@

Seed traits have functional significance in all levels of plant ecology, from population dynamics [@RN3043] to community assembly [@RN2942] and species distributions [@RN2942]. Recent discussions [@RN2352; @RN4655] highlighted the lack of reliable germination databases of wide geographical scope as a major limitation to produce a global synthesis of the seed ecological spectrum. Seed germination is the first major developmental transition in the life of a plant, and it has profound effects on the plant's ecology [@RN2384]. As such, the timing of this transition is controlled by a combination of environmental signals. Amongst these are temperature [@RN2249], diurnal temperature alternation [@RN2217], light [@RN4656] and seed dormancy inductors and relievers [@RN3063]. All of these signals interact to produce a coarse- and fine-scale regulation of germination timing, integrating inputs from both seasonal climatic cycles [@RN3132] and local environmental gradients [@RN2865]. The practical consequence of this is that the response of seeds to, for example, light will depend on other conditions set by the experimenter. This makes it difficult to summarise germination “traits” into a single value in a way comparable to seed mass, specific leaf area or plant height [@RN2923], and may explain the lack of global germination databases. Germination compilations with a biogeographical background, of which the prime example today is the cornerstone book of Baskin and Baskin [-@RN3214], only provide summary information, for instance the interpreted optimal germination temperature instead of the proportion of seeds germinated across a temperature gradient.

To fill this gap, this article presents *SylvanSeeds*, a first global database of raw germination data for an ecologically and biogeographically coherent unit: the Temperate Broadleaf and Mixed Forests biome of the northern hemisphere (*TBMFNH*). Deciduous forests are dominant in temperate latitudes with mild to cold winters and relatively warm and wet summers. In the northern hemisphere, they also form a coherent evolutionary and biogeographic unit, sharing a common Tertiary history until they became separated between North America, Asia and Europe [@RN4684]. At the same time, a relatively high number of classic seed biology research groups have worked within the *TBMFNH* areas, e.g. in the USA [@RN1045], the UK [@RN3273], Belgium [@RN656] and Japan [@RN1188]. To create *SylvanSeeds*, a systematic literature search [@RN2401] was applied to a list of frequent species representing the flora of the *TBMFNH*. This article makes the database accessible to the research community. Additionally, the *SylvanSeeds* shiny web app is presented to facilitate the exploration of the data.

@@

The list of frequent species (plus the synonyms recorded in the relevés) was incorporated into a Boolean search string, together with the words "(seed OR seeds) AND (dormancy OR germination)”. This string was searched in the *Thompson Reuters Web of Science* on 5 Mar 2019, returning 6,791 results. The processing of these results is described in a PRISMA flow diagram (**Supporting Information 1**). A first filter of the results by the relevance of the title retained 1,489 references. An effort was made to access the full text of all these references, using the following channels: (i) “Find Full Text” functionality in *EndNote X9*, (ii) online access to the journals using the institutional subscriptions of the University of Oviedo; (iii) request to the authors through *ResearchGate*; (iv) general search of *pdf* files in *Google* using the article details. Unfortunately, 236 references could not be accessed. Most of these belonged to smaller publishers not included in the subscriptions of the University of Oviedo, and to older journal issues which had not been digitalised. The resources of this project did not make it possible to further pursue these references, but they are included as a *BibTeX* file (**Supporting Information 2**) in case they can be processed in the future. The found texts were accessed to retrieve data for the database. At this stage, references were considered to be non-relevant if they (i) did not pertain to species in the original frequent species list; (ii) did not study germination in species monocultures (e.g. competition studies); (iii) did not report the minimal information needed (number of seeds sown, germination percentage and germination temperature). Records were also excluded when they pertained to special germination treatments that do not allow for general comparisons (i.e. use of germination promoters such as the plant hormone gibberellic acid; drought treatments, including polyethylene glycol solutions; application of heavy metals or other pollutants; smoke-related germination promoters such as karrikins). Of the accessed references, 639 were non-relevant (*BiBTeX* file in **Supporting Information 3**) and 614 provided relevant data (*BiBTeX* file in **Supporting Information 4**).

@@

For each relevant reference, three blocks of information were recorded. The first block described the plant material, including the species, the populations that had been sampled, the year of sampling (or the year of publication if that information was missing), the country, the geographical coordinates (if not provided in the reference, the closest available toponyms were searched in *Google Maps*; in some cases the only geographical information was the country, in these cases the coordinates of the capital city were recorded). The second block described the experimental conditions: experimental setting (greenhouse, incubator or room temperature), germination substrate and characteristics of the containers, seed storage, application of seed sterilization or nutrients, length of the germination incubations, use of stratification (none, cold [< 15ºC], warm [>= 15ºC] or combinations of cold and warm), use of scarification, photoperiod, maximum germination temperature, minimum germination temperature, and weighted average germination temperature. The third block contained the final germination proportion: the reported final germination percentages (retrieved from the text, tables or figures) and the reported number of replicates and seeds per replicate were used to calculate a count of seeds sown and a count of seeds germinated.

@@

The final database contains `r MSrecords` records (germination proportions for a given seed lot of a species, recorded in a set of experimental conditions) from 614 references. The plant materials had been collected across the Temperate Broadleaf and Mixed Forest biome and surrounding areas (**Fig. \@ref(fig:fig1)**), in both hemispheres. The oldest record was from 1920 and the top three contributing countries were the USA (`r MScountries[1, 2]`), the UK (`r MScountries[2, 2]`) and Japan (`r MScountries[3, 2]`). There were `r MSspecies` species represented, from `r MSfamilies` seed plant families. The total estimate of seeds used in the experiments was `r MSseeds`. The range of germination temperatures (weighted average of the daily thermoperiod) went from `r MSminT` to `r MSmaxT` ºC, with `r MSaltY` records of constant temperatures and `r MSaltN` of alternating temperatures. Light was used in `r MSlightY` records, darkness in `r MSlightN` and `r MSlightNA` did not provide information on this parameter. The experiments were performed with unstratified seeds in `r MSstratN` records, and of the rest, the majority (`r MSstratCold`) went through cold stratification. Scarification was applied to `r MSscarY` records.

@@

The database is provided as a *csv* file, comma separated, named **Supporting Information 5** (see online Supporting Information). The first row of the file contains the header data, with the following variables: *Taxon* (the original species names, as used in the references), *TPLName* (*The Plant List* species names), *Family* (the botanical family of the species), *Reference* (bibliographic source of the record), *Year* (year the seed lot was collected), *Country* (country where the seed lot was collected), *Population* (geographical information of the seed lot), *Latitude* (approximated latitude where the seed lot was collected, in decimal degrees), *Longitude* (approximated longitude where the seed lot was collected, in decimal degrees), *Dry_storage* (binary variable indicating whether the seed lot was kept at dry storage for more than a month between seed collection and start of the experiments), *Setting* (environs used to control germination temperature: either a greenhouse, a climatically-controlled incubator, or room temperature), *Sterilization* (note on surface sterilization treatments applied to the seed lot before the experiments), *Nutrients* (note on nutrient application to the germination substrate), *Substrate* (substrate used to hold the seeds during the germination incubation), *Container_type* (type of container used to hold the substrate and the seeds during the experiments), *Container_size* (dimensions of the germination containers), *Container_number* (number of germination containers used for the treatment), *Sown_by_container* (number of seeds sown in each container), *Incubation_days* (number of days between the start of the experiment, not including stratification, and the day when germinated seeds were counted), *Scarification* (binary variable indicating whether the seed lot was scarified before the test), *Stratification_days* (number of days the seed lot was exposed to any type of stratification, before the test), *Stratification_temperature* (temperature or temperatures used during the stratification treatment, in degrees Celsius), *Stratification_type* (type of stratification, which can be none, cold, warm or combinations of cold and warm), *Stratification* (binary variable indicating whether the seed lot was stratified or not before the test), *Light* (binary variable indicating whether the seed lot was germinated in light or in darkness), *Photoperiod* (number of hours of exposure to light in the daily photoperiod), *Alternating* (binary variable indicating whether the germination test was conducted under constant or alternating temperatures), *Tdif* (difference in degrees between the hottest and the coldest temperatures of the daily thermoperiod), *Tmax* (hottest temperature in the daily thermoperiod), *Tmin* (coldest temperature in the daily thermoperiod), *Tmean* (mean germination temperature, weighted by the length of each phase of the daily thermoperiod), *Temperature* (aggregation of the mean germination temperature in 5 ºC intervals), *Germinated* (count of seeds that germinated during the experiment), *Germinable* (count of seeds used in the experiment). Each row below the header represents a record for a seed lot germinated in a given set of experimental conditions. Presenting the response variable as a proportion (i.e. number of successes *Germinated*, number of trials *Germinable*) has important benefits for meta-analysis of the database, as proportions can be analysed directly using a GLM, and a variance term does not need to be specified since it is incorporated as part of the analysis [@RN4751].

@@

To facilitate the visualization of the database, the *SylvanSeeds* app was written using the *shiny* package [@RN4661]. It is publicly accessible at https://efernandezpascual.shinyapps.io/sylvanseeds/. The app uses the *tidyverse* package [@RN4662] to aggregate and show results for species and experimental treatments (i.e. aggregating all seed lots of the same species germinated in the same experimental conditions). To facilitate comparisons, germination temperatures are aggregated to 5 ºC intervals. When there is only one seed lot per species and combination of experimental conditions, the binomial 95% confidence interval is calculated using the Wilson method in the *binom* package [@RN2964]. When there is more than one seed lot per species and combination of experimental conditions, the aggregate proportion and binomial confidence intervals are calculated using binomial-normal meta-analysis models [@RN4663] as implemented in the package *metafor* [@RN2274]. By visiting the app, users can consult the available germination information for a species (**Fig. \@ref(fig:fig2)**), the origin of its seed lots, and the bibliographical references for the species.

@@

The database provided in this article, and the web app to visualize it, can have wide applicability in science and beyond. It can extend current trends in global analyses of plant traits at species [@RN3318] and community levels [@RN4664] to seed germination. The ecological determinants of seed germination are also valuable information for species distribution models [@RN3078]. The visualization of the database with the *SylvanSeeds* app can help plant ecologists select experimental treatments that are adequate for their experiments [@RN2999]. Outside of academia, germination data are useful for seed industries [@RN4665], restoration practitioners [@RN2241] and the implementation of regional schemes for seed-based landscape intervention [@RN4666]. The app is accessible to citizens in general who are interested in germinating wild plants. Finally, apart from the database itself, this article can bring two innovations to the seed ecology community, helping to advance the agenda of functional seed ecology [@RN4655]. First, the meta-analysis-inspired methodology used to compile the database can be extended to other biomes and lists of species, contributing to the creation of a global database for ecologically and biogeographically coherent floras. Second, the database and the app can serve as a standard in further efforts to compile and standardize seed germination data.

@@

@@

**Supporting Information 1** PRISMA 2009 flow chart describing the process of reference screening and inclusion. **Supporting Information 2** BibTeX bibliography listing the not found full texts.  **Supporting Information 3** BibTeX bibliography listing the non-relevant references.  **Supporting Information 4** BibTeX bibliography listing relevant references included in the *SylvanSeeds* database.  **Supporting Information 5** *SylvanSeeds* database in a single *.csv* file.

@@

All persons can use the database providing they cite this paper properly in any publications or in the metadata of any derived products that are produced using the database. The database is provided as Supporting Information. It can be visualized with the *SylvanSeeds* app at  https://efernandezpascual.shinyapps.io/sylvanseeds/. The code of the app is stored at (note: the GitHub repo is kept private until publication of the manuscript).
